---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# universals

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/poissonconsulting/universals.svg?branch=master)](https://travis-ci.com/poissonconsulting/universals)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/universals?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/universals)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
<!-- [![Tinyverse status](https://tinyverse.netlify.com/badge/universals)](https://CRAN.R-project.org/package=universals) -->
[![CRAN status](https://www.r-pkg.org/badges/version/universals)](https://cran.r-project.org/package=universals)
<!-- ![CRAN downloads](https://cranlogs.r-pkg.org/badges/universals) -->
<!-- badges: end -->

`universals` provides common model-fitting S3 generic methods 
missing from base R and the [`generics`](https://github.com/r-lib/generics) package to reduce package dependencies and conflicts.

## Philosophy

The methods are primarily designed to be used for Bayesian analyses that generate Markov Chain Monte Carlo (MCMC) samples but many of them can also be used for Maximum Likelihood (ML) and other types of analyses.

The names of the functions are based on the following definitions/concepts:

- A `term` is a single scalar numeric or integer value.
- A `parameter` is a scalar, vector, matrix or array of terms.
- An MCMC sample refers to a set of terms.
- The samples are arranged in one or more `chains` of the same length (number of `iterations`).
- The number of `simulations` is the product of the number of iterations and the number of chains.
- The number of `samples` is the product of the number of simulations and the number of `terms`.

## Installation

<!-- To install the latest release from [CRAN](https://cran.r-project.org) -->
```{r, eval=FALSE, echo=FALSE}
install.packages("universals")
```

To install the developmental version from [GitHub](https://github.com/poissonconsulting/universals)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/universals")
```

To install the latest developmental release from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```{r, eval=FALSE}
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("universals")
```

## Usage

`universals` is designed to be used by package developers.

As with [`generics`](https://github.com/r-lib/generics) it is recommended to import and re-export the generics of interest. For example, to provide a method for the  S3 `pars()` method, use the following `roxygen2` code:

``` {r, eval = FALSE}
#' @importFrom universals pars
#' @export
universals::pars
```


## Inspiration

The `universals` package is heavily inspired by the [`generics`](https://github.com/r-lib/generics) package.

It's possible that some of the methods migrate to that package in a future release.

## Contribution

Please report any [issues](https://github.com/poissonconsulting/universals/issues).

[Pull requests](https://github.com/poissonconsulting/universals/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/poissonconsulting/universals/blob/master/CODE_OF_CONDUCT.md).
By contributing, you agree to abide by its terms.
