---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# universals

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/poissonconsulting/universals/workflows/R-CMD-check/badge.svg)](https://github.com/poissonconsulting/universals/actions)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/universals/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/universals?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![CRAN status](https://www.r-pkg.org/badges/version/universals)](https://cran.r-project.org/package=universals)
<!-- ![CRAN downloads](https://cranlogs.r-pkg.org/badges/universals) -->
<!-- badges: end -->

`universals` provides common S3 generic methods 
for Bayesian Analyses to reduce package dependencies and conflicts.

## Philosophy

The methods are primarily designed to be used for Bayesian analyses that generate Markov Chain Monte Carlo (MCMC) samples but many of them can also be used for Maximum Likelihood (ML) and other types of analyses.

The names of the functions are based on the following definitions/concepts:

- A `term` is a single real or integer `value`.
- A `par` (short for parameter) is a scalar, vector, matrix or array of terms, ie a numeric atomic object.
- An MCMC sample refers to a set of terms.
- The samples are arranged in one or more `chains` of the same length (number of `iterations`).
- The number of `simulations` is the product of the number of iterations and the number of chains.
- The number of `samples` is the product of the number of simulations and the number of `terms`.

## Installation

<!-- To install the latest release from [CRAN](https://cran.r-project.org) -->
```{r, eval=FALSE, echo=FALSE}
install.packages("universals")
```

To install the developmental version from [GitHub](https://github.com/poissonconsulting/universals)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/universals")
```

## Usage

`universals` is designed to be used by package developers.

It is recommended to import and re-export the generics of interest. For example, to provide a method for the  S3 `pars()` method, use the following `roxygen2` code:

``` {r, eval = FALSE}
#' @importFrom universals pars
#' @export
universals::pars
```

## Inspiration

The `universals` package was inspired by the [`generics`](https://github.com/r-lib/generics) package.

## Contribution

Please report any [issues](https://github.com/poissonconsulting/universals/issues).

[Pull requests](https://github.com/poissonconsulting/universals/pulls) are always welcome.

## Code of Conduct

Please note that the universals project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.
